---
title: "Aides Tests"
author: "Ilysa Parra "
date: "December 4, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?

#Methods
The data for the Aides Tests is large, having over 4000 observations, 3 variables, and includes the data from the clinical trials in 2015. To make the data easier to use, we must trim it down. We will be using r code stored in a separate .r file to help do this. We start with the Aides Tests data from 2015 and then use the select function from the dplyr package to extract 3 variables that we must study in regards to our research question, we will only be using the data from South Carolina, Central Africa, and Korea. We still need to clean the data up a bit more. This was done in the following way: * We will subset each variable by sex to see if the drug is sex specific


##Graphical Results 

##South Carolina

We will subset the data by sex to see if the drug is sex specific.

###South Carolina Aids Results (Males)

```{r}
ScarolinaM <- filter(Scarolina,sex=="M")
barchartGC(~infected + group, data=ScarolinaM, type="percent")
```

More males infected with aids received the actual drug. Just slightly more males that have not been infected with aids received the placebo drug.

###South Carolina Aids Results (Females)

```{r}
ScarolinaF <- filter(Scarolina,sex=="F")
barchartGC(~infected + group, data=ScarolinaF, type="percent")
```

More females infected with aids received the placebo drug. Just slightly more females that were not infected with aids received the actual drug.

###South Carolina Aids Results (Both)

```{r}

barchartGC(~infected + group, data=Scarolina, type="percent")
```

As expected the people who got aides slightly more were the people who took the placebo.

# Central Africa

We will subset the data by sex to see if the drug is sex specific.


###Central Africa Aids Results (Males)
```{r}
cenAfricaM <- filter(cenAfrica,sex=="M")
barchartGC(~infected + group, data=cenAfricaM, type="percent")
```

More males infected with aids received the placebo drug. Half of the males that were not infected with aids received the actual drug and the other half received the placebo.

###Central Africa Aids Results (Females)
```{r}
cenAfricaF <- filter(cenAfrica,sex=="F")
barchartGC(~infected + group, data=cenAfricaF, type="percent")
```

More females were infected with aids received the placebo. Just slightly more females that were not infected with aids received the actual drug.

###Central Africa Aids Results (Both)
```{r}
barchartGC(~infected + group, data=cenAfrica, type="percent")
```

This drug helped to reduce the overall spread of Aids. More people got Aids when they took the placebo.

# Korea

We will subset the data by sex to see if the drug is sex specific.


###Korea Aids Results (Males)
```{r}
koreaM <- filter(korea,sex=="M")
barchartGC(~infected + group, data=koreaM, type="percent")
```
More males that were infected with aids received the placebo. Just slightly more males that were not infected with aids received the actual drug.

###Korea Aids Results (Females)
```{r}
koreaF <- filter(korea,sex=="F")
barchartGC(~infected + group, data=koreaF, type="percent")
```
More females that were infected with aids received the actual drug. Just slightly more females that were not infected with aids received the placebo.

###Korea Aids Results (Both)
```{r}
barchartGC(~infected + group, data=korea, type="percent")
```
Based on the graph the people who had the placebo got aids much more than the drug. This drug worked to prevent the spread of aids.

Based on our graphical results, the relationship shown between the groups from the data is that the groups receiving the drug are not only sex specific, but also disease specific. You can see that sometimes there were more people that have not been infected with aids received either the actual drug or placebo. This was to see if the actual drug would be able to prevent aids completely.

#Numerical Results

## South Carolina

###Females
```{r}
ScarolinaF_table <- xtabs(~infected + group, data = ScarolinaF)
rowPerc(ScarolinaF_table)

```
More females (61.17%) that were infected with aids received a placebo drug. More females (50.55%) that were not infected with aids received the actual drug in hopes to prevent it.

###Males
```{r}
ScarolinaM_table <- xtabs(~infected + group, data = ScarolinaM)
rowPerc(ScarolinaM_table)
```
More males (57.35%) that were infected with aids received the actual drug. More males (50.48%) that were not infected with aids received the placebo drug.

###Both
```{r}
Scarolina_table <- xtabs(~infected + group, data = Scarolina)
rowPerc(Scarolina_table)
```
More people overall that recieved the placebo got aids.

##Central Africa

###Female
```{r}
cenAfricaF_table <- xtabs(~infected + group, data = cenAfricaF)
rowPerc(cenAfricaF_table)
```
More females (53.45%) that were infected with aids received the placebo drug. More females (50.17%) that were not infected with aids received the actual drug.

###Males
```{r}
cenAfricaM_table <- xtabs(~infected + group, data = cenAfricaM)
rowPerc(cenAfricaM_table)
```
More males (50.53%) that were infected with aids received the placebo drug. More males (50.02%) that were not infected with aids received the actual drug.

###Both
```{r}
cenAfrica_table <- xtabs(~infected + group, data = cenAfrica)
rowPerc(cenAfrica_table)
```
The results indicate that the drug was effective in preventing aids, as only 47% got aids compared to the 52% that took the placebo.

##Korea

###Females
```{r}
koreaF_table <- xtabs(~infected + group, data = koreaF)
rowPerc(koreaF_table)
```
More females (65.43%) that were infected with aids received the actual drug. More females (50.57%) that were not infected with aids received the placebo.

###Males
```{r}
koreaM_table <- xtabs(~infected + group, data = koreaM)
rowPerc(koreaM_table)
```
More males (67.32%) that were infected with aids received the placebo drug. More males (51.25%) that were not infected with aids received the actual drug.

###Both 
```{r}
korea_table <- xtabs(~infected + group, data= korea)
rowPerc(korea_table)
```
The results show that the drug worked well in preventing aids because only 44% of people got aids, while 55% of people got aids while taking the placebo.

###Discussion on Numerical Results
In South Carolina and Central Africa, more females that were infected with aids received a placebo drug. But in Korea, more females with aids received the actual drug. In Central Africa and Korea, more males that were infected with aids received the placebo drug whereas more males in South Carolina received the actual drug. The drug may be sex specific, but it seems more like a geographical issue instead of a sex issue. We will perform a chisquare test to help determine our answer for our research question.


#Inferential Results

##South Carolina

###Both 
Null- The aids drug is not effective. (Independent)

Alternative- The aids drug is effective.
```{r}
chisqtestGC(Scarolina_table)
```
The p-value is 89%, we accept the null hypothesis. We can assume that the drug is not effective.

###Males
Null- The aids drug is not specific to males. (Independent)

Alternative- The aids drug is specific to males.
```{r}
chisqtestGC(ScarolinaM_table)
```
The P-value is 9%, greater than 5%, so we will accept the null hypothesis and assume that the drug is not specific to males.

###Females
Null- The aids drug is not specific to females. (Independent)

Alternative- The aids drug is specific to females.
```{r}
chisqtestGC(ScarolinaF_table)
```
The P-value is 2% which is obviously less than 5%. Due to this we will reject the null hypothesis and assume that the aids drug is specific to females.


##Central Africa

###Both
Null- The aids drug is not effective. (Inependent)

Alternative-  The aids drug is effective.
```{r}
chisqtestGC(cenAfrica_table)
```
The P-value is 57%, accepting the null hypothesis that the drug in Central Africa is not effective


###Males
Null- The aids drug is not specific to males. (Independent)

Alternative- The aids drug is specific to males.
```{r}
chisqtestGC(cenAfricaM_table)
```
The P-value is 1, we accept the null hypothesis and assume that the drug is independent and not specific to males.


###Females
Null- The aids drug is not specific to females. (Independent)

Alternative- The aids drug is specific to females
```{r}
chisqtestGC(cenAfricaF_table)
```
The P-value is 50%, we accept the null hypothesis and assume that the drug is not specific to females.



##Korea

###Both
Null- The aids drug is not effective. (Inependent)

Alternative- The aids drug is effective.
```{r}
chisqtestGC(koreaF_table)
```
The P-value is 69%, we will accept the null hypothesis and assume that the drug is independent and not effective.



###Males
Null- The aids drug is not specific to males. (Inependent)

Alternative- The aids drug is specific to males.
```{r}
chisqtestGC(koreaM_table)
```
The P-value is zero, we reject the null hypothesis and assume that the drug is specific to males.



###Females
Null-The aids drug is not specific to females. (Inependent)

Alternative- The aids drug is specific to females.
```{r}
chisqtestGC(koreaF_table)
```
The P-value is 0 assuming that the drug is specific to females.

#Inferential Conclusion
Regarding each geographical location, more people that have have aids received the palcebo drug whereas more that did not have aids received the actual drug. In South Carolina and Central Africa, more females that were infected with aids received a placebo drug. But in Korea, more females with aids received the actual drug. In Central Africa and Korea, more males that were infected with aids received the placebo drug whereas more males in South Carolina received the actual drug. The drug may be sex specific, but it seems more like a geographical issue instead of a sex issue. We will perform a chisquare test to help determine our answer for our research question.


#Conclusion
We made bar charts and numerical tables for each location specific to different drug. In the chisquare tests we learn that all three drugs are not effective in preventing aids. We do learn, however, that the drugs can be sex specific. In South Carolina, this drug is specific to females and that it may have had a positive influence on them. In Central Africa we learn that the drug is not specific to either sex and may have had a negative influence on both males and females. In Korea we learn that the drug is specific to males and females and may have had a positive influence on both groups.

